%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables


% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained} 
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.1145/3283458.3283494}

% ISBN
\acmISBN{978-1-4503-6558-1/18/12}

%Conference
\acmConference[AfriCHI '18]{2nd African Conference for Human Computer Interaction}{December 3--7, 2018}{Windhoek, Namibia}
\acmBooktitle{2nd African Conference for Human Computer Interaction (AfriCHI '18), December 3--7, 2018, Windhoek, Namibia}
\copyrightyear{2018} 
\acmYear{2018} 
\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\begin{document}
\title{The Interplay Between Emotion and Trust in Technology  }
\author{Ighoyota B. Ajenaghughrure}
\affiliation{%
  \institution{School of Digital Technologies, Tallinn University}
  \streetaddress{Narva Mnt. 25}
  \city{Tallinn}
  \state{Harju}
  \postcode{10120}
 \country{Estonia}}
\email{Ighoyota@tlu.ee}

\author{Sonia Claudia Da Costa Sousa}
\affiliation{%
  \institution{School of Digital Technologies, Tallinn University}
  \streetaddress{Narva Mnt. 25}
  \city{Tallinn}
  \state{Harju}
  \postcode{10120}
 \country{Estonia}}
\email{scs@tlu.ee}

\author{David Ribeiro Lamas}
\affiliation{%
  \institution{School of Digital Technologies, Tallinn University}
  \streetaddress{Narva Mnt. 25}
  \city{Tallinn}
  \state{Harju}
  \postcode{10120}
 \country{Estonia}}
\email{drl@tlu.ee}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Ajenaghughrure et al.}


\begin{abstract}
As technology evolves, exhibiting human-like characteristics. it is becoming part of human daily activities with possibility of high degrees of dependency, due to its adaptation to users . For example merely speaking to a smart phone to make a call or send a text. The new challenge of persuading users to change behavior such as low adoption of these technologies has emerged. Because little effort is required to use and users also know little or nothing about how they operate.
 Trust is a key concept to study. As it can mitigate the present, discussed risk and uncertainty associated with present and future technologies. In addition to trust, emotion is also a key indicator for persuading users to changing behavior toward technical artifact.
Therefore, this research focuses on unraveling the interplay between emotion and trust of users when interacting with human-like technologies. The contribution of this research is the development of conceptual mapping of various emotional affect and trust in technology using psychometric and physiological evidences. This can further the understanding of persuasive application development by taking not just trust factors into account or emotional factors alone, but the relationship between these two indicators

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121.10003122</concept_id>
<concept_desc>Human-centered computing~HCI design and evaluation methods</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10011748</concept_id>
<concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10011749</concept_id>
<concept_desc>Human-centered computing~Laboratory experiments</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~HCI design and evaluation methods}
\ccsdesc[500]{Human-centered computing~Empirical studies in HCI}
\ccsdesc[100]{Human-centered computing~Laboratory experiments}


\keywords{Emotion, Trust, Human-like Technologies, Behavior, HCI}


\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
